Diffantom: a whole-brain diffusion MRI phantom derived from a real dataset

### 2015-08-12 paper/main.tex
Starting with #22. Close #20

Since the gradient scheme can be set by the user, \emph{diffantom} can be seen as a mean to translate the so-called
  \emph{b-matrix} of the \gls*{hcp} to any target scheme.
A second recommended use case of the simulation workflow is its integration in assessment frameworks
  (\autoref{fig:figure2}, box A) for the unit testing of algorithms, the integration tests of
  modules in workflows and the full validation of pipelines.
The \emph{diffantom} enables the following evaluations of connectivity pipelines:
\begin{itemize}
  \item Studies on the impact of different diffusion sampling schemes on the local micro-structure
  model of choice and on the subsequent global tractography outcome.
  \item Assessment of sensitivity and robustness to imaging artifacts (noise, \acrlong{pve} and \glslines{csf} contamination,
    susceptibility-derived warping, Eddy-currents-derived distortions, etc.) at both local and global levels.
  \item Characterizing the \acrfull*{roc} of connectivity pipelines.
  \item Generation of synthetic connectivity networks to test graph theory analyses.
  \item Simulation of pathological brains (e.g. tumors as in \cite{kaus_simulation_2000}).
\end{itemize}

>>>>

We recommend \emph{Diffantom} as ground-truth in assessment frameworks (\autoref{fig:figure2}, box A)
  for the unit testing of algorithms, the integration tests of modules in workflows and the full
  validation of pipelines:
\begin{itemize}
  \item Investigating the impact of different diffusion sampling schemes on the local microstructure
    model of choice and on the subsequent global tractography outcome.
  Since the gradient scheme can be set by the user, \emph{diffantom} can be seen as a mean to translate the so-called
  \emph{b-matrix} of the source dataset to any target scheme.
  \item Assessment of sensitivity and robustness to imaging artifacts (noise, \acrlong{pve} and \glslines{csf} contamination,
    susceptibility-derived warping, Eddy-currents-derived distortions, etc.) at both local and global levels.
  \item Characterizing the \acrfull*{roc} of connectivity pipelines.
  \item Generation of synthetic connectivity networks to test graph theory analyses.
  \item Simulation of pathological brains (e.g. tumors as in \cite{kaus_simulation_2000}).
\end{itemize}
